### 2020-03-28 writeup/setup.tex
reorg
add intro

@@

\todo{setup motivation and notations}

>>>>

\section{Introduction}

Multi-task learning that is applied on heterogenous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional linear regression setting.
\begin{enumerate}
	\item {\bf Negative transfer:} we establish a fundamental limit that is caused by model shift.
	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
	\item {\bf De-noising effect of MTL:} we show that multi-task transfer has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
\end{enumerate}

@@

\todo{setup motivation and notations}
We would like to get insight on how covariate and model shifts affect the rate of transfer.
For the case of two tasks, we can get precise rates using random matrix theory.
For the sake of clarity, we call task 1 the source task and task 2 the target task,
i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
